Generative Models for scRNA

### 2018-04-02 generativemodelsforscrna/outline.tex
corrected bug

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/Z1gn}
\caption{\label{fig:Z1gn}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/resids}
\caption{\label{fig:resids}}
\end{figure}

These results are actually fairly encouraging.  Mostly it looks basically like white noise.  However, we do see that for some genes the $p$ values are almost always near 1: these are genes which express essentially never, and so have a high chance of turning off, and so their $p$ value is nearly $1$ whenever they are off, which is virtually always.  If we restrict ourselves to those genes whose average probability of going off is less than 20\%, we obtain Figure \ref{fig:residslesszeros}.

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/residslesszeros}
\caption{\label{fig:residslesszeros}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/Z1gn}
\caption{Colors indicate gene expression level. \label{fig:Z1gn}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/resids}
\caption{A $p$-value residual plot.\label{fig:resids}}
\end{figure}

These results are actually fairly encouraging.  Mostly it looks basically like white noise.  However, we do see that for some genes the $p$ values are almost always near 1: these are genes which express essentially never, and so have a high chance of turning off, and so their $p$ value is nearly $1$ whenever they are off, which is virtually always.  If we restrict ourselves to those genes whose average probability of going off is less than 20\%, we obtain Figure \ref{fig:residslesszeros}.  We do this in Figure \ref{fig:residslesszerosFA}.

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/residslesszeros}
\caption{If we include only genes that express at least 80\% of the time, the $p$-value residual plot looks less structured.\label{fig:residslesszeros}}
\end{figure}

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/residslesszerosFA}
\caption{Using Factor Analysis for our model (with 16 factors), we see more significant underfitting.  (Here we include only genes that express at least 80\% of the time)\label{fig:residslesszerosFA}}
\end{figure}
